The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-13 thesis/paper.tex
Added table to show counts of types. Included some brief explanations of the types of change for the introduction

              \textbf{Type}                              & \textbf{Explanation}    \\ \midrule
              Corrective    & [Explanation]                      \\ \hline
              Reductive     & [Explanation]                     \\ \hline
              Adaptive      & [Explanation]                      \\ \hline
              Performance   & [Explanation]                     \\ \hline
              Preventive    & [Explanation]                      \\ \hline
              Groomative    & [Explanation]                      \\ \hline
              Updative      & [Explanation]                     \\ \hline
              Reformative   & [Explanation]                     \\ \hline
              Evaluative    & [Explanation]                     \\ \hline
              Consultive    & [Explanation]                     \\ \hline
              Training      & [Explanation]                     \\

@@

All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}. In total, thirteen unique changes were found.

@@

>>>>

              \textbf{Type}                              & \textbf{Explanation}    \\ \midrule
              Corrective    & Corrections of functionality                   \\ \hline
              Reductive     & Reductions of functionality                    \\ \hline
              Adaptive      & Inclusion of new Technology                    \\ \hline
              Performance   & Improvements to Performance                    \\ \hline
              Preventive    & Improvements to future maintainability         \\ \hline
              Groomative    & Improvements to maintainability                \\ \hline
              Updative      & Updates to documentation                       \\ \hline
              Reformative   & Changes to documentation                       \\ \hline
              Evaluative    & Inspection activities                          \\ \hline
              Consultive    & Consultations activities                       \\ \hline
              Training      & Training activities                            \\

@@

All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}. In total, thirteen unique changes were found. The count of change types is shown in table \ref{table:type_counts}.

\begin{table}
       \centering
       \begin{tabular}[ht]{l|c|c}
              \toprule

              \textbf{Type}                              & \textbf{Main Types}   &\textbf{Sub Types} \\ \midrule
              Enhancive     & 7 & 0                     \\ \hline
              Corrective    & 0 & 0                     \\ \hline
              Reductive     & 1 & 0                    \\ \hline
              Adaptive      & 1 & 0                     \\ \hline
              Performance   & 0 & 0                    \\ \hline
              Preventive    & 2 & 0                     \\ \hline
              Groomative    & 0 & 5                     \\ \hline
              Updative      & 1 & 1                    \\ \hline
              Reformative   & 1 & 1                     \\ \hline
              Evaluative    & 0 & 0                    \\ \hline
              Consultive    & 0 & 0                    \\ \hline
              Training      & 0 & 0                    \\

       \end{tabular}
       \caption{Identified Change Types}
       \label{table:type_counts}
\end{table}

@@

%Implications for Industry
%Implications for Academia
%Future work / suggestions based on this RQ?
